Muir et al.---American Journal of Botany 2022---Appendix S1

### 2022-07-10 ms/si.Rmd
archive

---
title: 'Supporting Information'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

@@

```{r df_pop_lm, eval=TRUE, echo=FALSE}
knitr::kable(df_pop_lm, format = "markdown", caption = "\\label{tab:df_pop_lm} Between-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival ($\\text{logit}(p_\\text{surv})$). The parameters are the linear regression slope and intercept. Point estimates and 95\\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.", label = NA)
```

>>>>

---
title: 'Muir et al.—American Journal of Botany 2022—Appendix S1'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

@@

```{r df_pop_lm, eval=TRUE, echo=FALSE}
knitr::kable(df_pop_lm, format = "markdown", caption = "\\label{tab:df_pop_lm} Among-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival ($\\text{logit}(p_\\text{surv})$). The parameters are the linear regression slope and intercept. Point estimates and 95\\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.", label = NA)
```

### 2022-07-10 ms/si.tex
verified make
archive

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supporting Information},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

\title{Supporting Information}
\author{}
\date{\vspace{-2.5em}}

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_pop_lm} Between-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & \(4.01~(2.97,~5.51)\) \\
North & slope & \(-0.444~(-0.675,~-0.304)\) \\
South & intercept & \(4.82~(3.73,~6.24)\) \\
South & slope & \(-0.344~(-0.556,~-0.208)\) \\
\bottomrule
\end{longtable}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Muir et al.---American Journal of Botany 2022---Appendix S1},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

\title{Muir et al.---American Journal of Botany 2022---Appendix S1}
\author{}
\date{\vspace{-2.5em}}

@@

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_pop_lm} Among-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & \(4.01~(2.97,~5.51)\) \\
North & slope & \(-0.444~(-0.675,~-0.304)\) \\
South & intercept & \(4.82~(3.73,~6.24)\) \\
South & slope & \(-0.344~(-0.556,~-0.208)\) \\
\bottomrule
\end{longtable}

### 2022-07-10 ms/tables-and-captions.tex
archive

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Muir et al.---American Journal of Botany 2022---Appendix S1},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

\title{Muir et al.---American Journal of Botany 2022---Appendix S1}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

@@

\setstretch{1}
\renewcommand\thefigure{S\arabic{figure}}    
\renewcommand\thetable{S\arabic{table}}    
\setcounter{figure}{0}    
\setcounter{table}{0}

\begin{figure}[ht]
  \includegraphics{figures/range-map.pdf}
  \caption{Source populations are distributed through the range of \textit{Mimulus cardinalis}. Dark grey points are occurrence records located throughout California and Oregon, USA (Muir and Angert 2017). Source populations for this study are labeled with colored points. Transplant gardens are labeled with bold font in white boxes.}
  \label{fig:range-map}
\end{figure}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figures/pp_check_germ.pdf}
  \caption{(Caption next page.)}
  \label{fig:pp_check}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure} [t!]
  \caption{(Previous page.) Posterior predictive check of germination rate from discretized log-normal model for the South cohort (left facets) and North cohort (right facets). Each histogram in gray bars is for one of five \textit{M. cardinalis} populations arranged from northern (top) to southern (bottom). The black points are median values from randomly simulated data sets drawn from each iteration of the posterior distributions. Lines indicate the 95\% confidence interval but are usually too narrow to be seen behind the point estimates. A close match between observations and posterior predictions indicate that the model adequately describes the distribution of the data.}
\end{figure}

\begin{figure}[ht]
  \includegraphics[width=\textwidth]{figures/climate.pdf}
  \caption{The average temperature during the 2015-16 experiment (lines) was warmer than the historical normal from 1961-1990 (points). The $y$-axis is the average temperature for a season in the southern (solid line) and northern (dashed line) garden. Points are the average seasonal temperature for the 1961-1990 normal for each population source location. Population color is arranged from orange to blue by latitude of origin from south to north. Season is along the $x$-axis. Autumn encompasses September-November; winter encompasses December-February; spring encompasses March-May. All down-scaled climate are from ClimateNA (see Materials and Methods).}
  \label{fig:climate}
\end{figure}

\clearpage

\begin{longtable}[]{@{}ll@{}}
\caption{\label{tab:vc_table_germ} We decomposed variance in time to germination among populations (\(V_\text{pop}\)), additive genetic differences among individuals in the base population (\(V_G\)), maternal effects (\(V_M\)) experimental blocks within the greenhouse (Block), and residual environmental variance (\(V_E\)). The broad-sense heritability \(H^2\) is the proportion of variance contributed by \(V_G\). Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Parameter & Median (95\% CI) \\
\midrule
\endhead
\(V_\text{pop}\) & \(0.142~(0.0772,~0.232)\) \\
\(V_G\) & \(0.16~(0.112,~0.235)\) \\
\(V_M\) & \(0.036~(0.0243,~0.0546)\) \\
Block & \(0.0355~(0.0238,~0.0569)\) \\
\(V_E\) & \(0.251~(0.244,~0.26)\) \\
\(H^2\) & \(0.33~(0.257,~0.422)\) \\
\bottomrule
\end{longtable}

\clearpage

\blandscape

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2762}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.0667}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1429}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.5143}}@{}}
\caption{\label{tab:vc_table_surv} We decomposed variance in winter survival (\(\text{logit}(p_\text{surv})\)) among populations (\(V_\text{pop}\)), additive genetic differences among individuals in the base population (\(V_\text{G}\)), experimental blocks in the field (Block), and residual environmental variance (\(V_\text{E}\)) for the North and South garden separately. The broad-sense heritability \(H^2\) is the proportion of variance contributed by \(V_G\). Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Population
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Garden
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Median (95\% CI)
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Population
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Garden
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Parameter
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Median (95\% CI)
\end{minipage} \\
\midrule
\endhead
Sweetwater River & North & \(H^2\) & \(0.00742~(0.00208,~0.0211)\) \\
Sweetwater River & North & \(V_\text{pop}\) & \(0.00744~(0.00429,~0.0109)\) \\
Sweetwater River & North & \(V_E\) & \(0.186~(0.144,~0.219)\) \\
Sweetwater River & North & \(V_G\) & \(0.0014~(0.000327,~0.00415)\) \\
Sweetwater River & North & Block & \(0.0014~(0.000327,~0.00415)\) \\
West Fork Mojave River & North & \(H^2\) & \(0.00787~(0.00219,~0.0212)\) \\
West Fork Mojave River & North & \(V_\text{pop}\) & \(0.00744~(0.00429,~0.0109)\) \\
West Fork Mojave River & North & \(V_E\) & \(0.201~(0.16,~0.228)\) \\
West Fork Mojave River & North & \(V_G\) & \(0.00167~(0.000379,~0.00453)\) \\
West Fork Mojave River & North & Block & \(0.00167~(0.000379,~0.00453)\) \\
North Fork Middle Tule River & North & \(H^2\) & \(0.0072~(0.00195,~0.0208)\) \\
North Fork Middle Tule River & North & \(V_\text{pop}\) & \(0.00744~(0.00429,~0.0109)\) \\
North Fork Middle Tule River & North & \(V_E\) & \(0.176~(0.132,~0.212)\) \\
North Fork Middle Tule River & North & \(V_G\) & \(0.00132~(0.000292,~0.00394)\) \\
North Fork Middle Tule River & North & Block & \(0.00132~(0.000292,~0.00394)\) \\
Little Jamison Creek & North & \(H^2\) & \(0.00854~(0.00236,~0.0241)\) \\
Little Jamison Creek & North & \(V_\text{pop}\) & \(0.00744~(0.00429,~0.0109)\) \\
Little Jamison Creek & North & \(V_E\) & \(0.224~(0.185,~0.241)\) \\
Little Jamison Creek & North & \(V_G\) & \(0.00194~(0.000487,~0.00563)\) \\
Little Jamison Creek & North & Block & \(0.00194~(0.000487,~0.00563)\) \\
Rock Creek & North & \(H^2\) & \(0.00894~(0.00256,~0.0259)\) \\
Rock Creek & North & \(V_\text{pop}\) & \(0.00744~(0.00429,~0.0109)\) \\
Rock Creek & North & \(V_E\) & \(0.242~(0.228,~0.248)\) \\
Rock Creek & North & \(V_G\) & \(0.00221~(0.000632,~0.00642)\) \\
Rock Creek & North & Block & \(0.00221~(0.000632,~0.00642)\) \\
Sweetwater River & South & \(H^2\) & \(8.91 \times 10^{-5}~(5.89 \times 10^{-6},~0.00448)\) \\
Sweetwater River & South & \(V_\text{pop}\) & \(0.00147~(0.000618,~0.00287)\) \\
Sweetwater River & South & \(V_E\) & \(0.0683~(0.044,~0.107)\) \\
Sweetwater River & South & \(V_G\) & \(8.24 \times 10^{-6}~(3.32 \times 10^{-7},~0.000341)\) \\
Sweetwater River & South & Block & \(0.00573~(0.00174,~0.0187)\) \\
West Fork Mojave River & South & \(H^2\) & \(9.34 \times 10^{-5}~(5.95 \times 10^{-6},~0.00545)\) \\
West Fork Mojave River & South & \(V_\text{pop}\) & \(0.00147~(0.000618,~0.00287)\) \\
West Fork Mojave River & South & \(V_E\) & \(0.0798~(0.0481,~0.117)\) \\
West Fork Mojave River & South & \(V_G\) & \(8.89 \times 10^{-6}~(4.7e-07,~0.000579)\) \\
West Fork Mojave River & South & Block & \(0.00867~(0.00225,~0.0244)\) \\
North Fork Middle Tule River & South & \(H^2\) & \(0.000111~(6.73 \times 10^{-6},~0.00571)\) \\
North Fork Middle Tule River & South & \(V_\text{pop}\) & \(0.00147~(0.000618,~0.00287)\) \\
North Fork Middle Tule River & South & \(V_E\) & \(0.0898~(0.0645,~0.125)\) \\
North Fork Middle Tule River & South & \(V_G\) & \(1.24 \times 10^{-5}~(5.37 \times 10^{-7},~0.000569)\) \\
North Fork Middle Tule River & South & Block & \(0.0102~(0.00369,~0.0302)\) \\
Little Jamison Creek & South & \(H^2\) & \(0.000109~(7.4e-06,~0.00653)\) \\
Little Jamison Creek & South & \(V_\text{pop}\) & \(0.00147~(0.000618,~0.00287)\) \\
Little Jamison Creek & South & \(V_E\) & \(0.0988~(0.0633,~0.136)\) \\
Little Jamison Creek & South & \(V_G\) & \(1.47 \times 10^{-5}~(6.92 \times 10^{-7},~0.000819)\) \\
Little Jamison Creek & South & Block & \(0.0126~(0.00426,~0.0352)\) \\
Rock Creek & South & \(H^2\) & \(0.000148~(1.03 \times 10^{-5},~0.00803)\) \\
Rock Creek & South & \(V_\text{pop}\) & \(0.00147~(0.000618,~0.00287)\) \\
Rock Creek & South & \(V_E\) & \(0.133~(0.103,~0.161)\) \\
Rock Creek & South & \(V_G\) & \(2.54 \times 10^{-5}~(1.49 \times 10^{-6},~0.00144)\) \\
Rock Creek & South & Block & \(0.0239~(0.0108,~0.0507)\) \\
\bottomrule
\end{longtable}

\elandscape

\clearpage

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_pop_lm} Among-population directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & \(4.01~(2.97,~5.51)\) \\
North & slope & \(-0.444~(-0.675,~-0.304)\) \\
South & intercept & \(4.82~(3.73,~6.24)\) \\
South & slope & \(-0.344~(-0.556,~-0.208)\) \\
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}lll@{}}
\caption{\label{tab:df_ind_lm} Genotypic directional selection coefficient estimates and confidence intervals. In both North and South gardens, we estimated selection on time to germination (log-mean scale) caused by increased winter survival (\(\text{logit}(p_\text{surv})\)). The parameters are the linear regression slope and intercept. Point estimates and 95\% confidence intervals (CI) are estimated from the median and quantiles of the posterior distribution.}\tabularnewline
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endfirsthead
\toprule
Garden & Parameter & Median (95\% CI) \\
\midrule
\endhead
North & intercept & \(-0.00151~(-0.0345,~0.0255)\) \\
North & slope & \(-0.08~(-0.27,~0.0243)\) \\
South & intercept & \(0.00059~(-0.0156,~0.0244)\) \\
South & slope & \(-0.000876~(-0.11,~0.1)\) \\
\bottomrule
\end{longtable}

\clearpage

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

\author{}
\date{\vspace{-2.5em}}

\begin{document}

@@

\setstretch{1.5}
\hypertarget{tables}{%
\section{Tables}\label{tables}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.4265}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1471}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1765}}
  >{\centering\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.2500}}@{}}
\caption{\label{tab:focal_pops} Source populations, including the name of the drainage where the seeds were collected, the latitude, longitude, and elevation in meters above sea level (mas).}\tabularnewline
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Source population
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Latitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Longitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Elevation (mas)
\end{minipage} \\
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{\linewidth}\raggedright
Source population
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Latitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Longitude
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
Elevation (mas)
\end{minipage} \\
\midrule
\endhead
Sweetwater River & \(32.900\) & \(-116.585\) & \(1180\) \\
West Fork Mojave River & \(34.284\) & \(-117.378\) & \(1120\) \\
North Fork Middle Tule River & \(36.201\) & \(-118.759\) & \(926\) \\
Little Jamison Creek & \(39.743\) & \(-120.704\) & \(1603\) \\
Rock Creek & \(43.374\) & \(-122.957\) & \(326\) \\
\bottomrule
\end{longtable}

\hypertarget{figure-captions}{%
\section{Figure captions}\label{figure-captions}}

\begin{figure} [ht]
  \caption{Germination rate and survival differ among source populations of \textit{Mimulus cardinalis}. Source populations are arrayed along the $x$-axis by latitude of origin from south to north. In both panels, the violins represent the posterior distribution of the population trait value and the bars are the median. Each black point is the median trait value for one of the individuals in the base population. Connecting letters above violins indicate populations that significantly different or not. The 95\% confidence interval for difference among populations includes 0 for those with the same letter. a. The northernmost populations germinate days later than southern populations in the same greenhouse environment. b. In both South (solid linetype around violin) and North (dashed linetype around violin) gardens, source populations originating from the south had higher probability of winter survival than northern source populations. However, the overall survival was greater in the South garden, such that even the northernmost source population (Rock Creek) had higher survival in the South than in the North garden.}
\end{figure}

\begin{figure}[ht]
  \caption{Estimated variance components and heritability of germination rate in units of log(days)$^2$. a. The variance in germination rate among source populations $V_\text{pop}$ is comparable to the genetic variation within populations $V_G$. The variance among Blocks and maternal parent ($V_M$) in the greenhouse is substantially lower whereas the unexplained environmental variance is higher $V_E$. b. This results a moderate heritability $H^2$ which is $V_G / V_P$. The point estimates are the median of the posterior distribution; thick lines are $80$\% confidence intervals; and thin lines are the $95$\% confidence intervals.}
  \label{fig:h2-germ}
\end{figure}

\begin{figure}[ht]
  \caption{Estimated variance components and heritability of winter survival in units of $p^2_\text{surv}$. The top row of facets are estimates from the North garden; the bottom row of facets are estimates from the South garden. On the $x$-axis, the source populations are arranged from left (orange) to right (blue) by latitude going from south to north. The right-most facet ($V_\text{pop}$ is grey because it is the variance among populations. On the $y$-axis (log$_{10}$-transformed for visual clarity) is the variance or heritability ($H^2$) depending on the facet. In both gardens, the unexplained environmental ($V_E$) is higher than the variance contributed by field Block, genetic variance ($V_E$), or variance among source populations ($V_\text{pop}$). Hence, the $H^2$ is very low in both gardens. The point estimates are the median of the posterior distribution; thick lines are $80$\% confidence intervals; and thin lines are the $95$\% confidence intervals.}
  \label{fig:h2-surv}
\end{figure}

\begin{figure}[ht]
  \caption{Directional selection favor faster germination among but not within source populations. In both South (grey ribbon) and North (white ribbon) gardens, source populations that germinated faster ($x$-axis) also had higher winter survival ($y$-axis). The larger solid points are the population average estimated from the median of the posterior distribution; smaller translucent points are the genotypic mean trait values within populations. The solid line is regression between germination rate and winter survival among populations estimated from the median of the posterior distribution; the genotypic regression results are not shown in this figure. The ribbon within the thinner black lines is the $95$\% confidence interval of the regression.}
  \label{fig:selection}
\end{figure}
